A Transdiciplinary approach to develop a new spectral numerical coastal-flow model based on natural passive macroalgal rafting phenenomea to shed light on ambient and stochastic dispersal and connectivity of nearshore and offshore marine communities around the coast of South Africa: Combining ecolog

### 2019-08-21 literature_review.Rmd
started added section on measuring waves. tested word output. adding template to test next. some intial figures added to figures folder.

---
title: "Literature review"
author: "Ross Coppin"
date: "20/08/2019"
output: word_document
---
# Summary

@@

# Hydrodynamic modelling

@@

# Delft-3D numerical suite

@@

## Delft-3D WAVE

@@

## Delft-3D FLOW

>>>>

---
title: "A Transdiciplinary approach to develop a new spectral numerical coastal-flow model based on natural passive macroalgal rafting phenenomea to shed light on ambient and stochastic dispersal and connectivity of nearshore and offshore marine communities around the coast of South Africa: Combining ecology and 3D hyperspectral hydrodynamic modelling."
author: "Ross Coppin"
date: "20/08/2019"
output: 
  word_document: 
    fig_caption: yes
---

```{r include=FALSE}
library(png)
library(grid)
```

# Summary

@@

## Measuring waves

Waves are often thought of as an elevation of the sea surface from a specific point over a period of time but this is obvisiously not he case. This is known as *surface elevation* and is the instaneous elevation of the sea surface abouve a specific point in a time record (see figure ???). Although surface elevation does not represent a wave, it can be used to create a wave profile. This is achieved by profiling the the surface elevation between two successive *downward zero-crossings* (see figure ??).

```{r surface elevation figures, echo=FALSE, warning=FALSE, fig.cap="The definition of a wave in a time record of the surface elevation with downward zero-crossings (upper panel) and upward zero-crossings (lower panel)."}

surface_elevation <- readPNG("figures/surface_elevation_waves.png")
grid.raster(surface_elevation)
```

Waves are complex and various approaches, techniques and devices have been developed in order to measure waves effectively. One of the ways that has been used extensivley in the past but less so today, are visual estimates which can be used to characterise *significant swell height* (Hs) and *significant swell period* (Tp). Visual estimates use 15 - 20 of the most well defined, higher waves of a number of wave groups to characterise Hs and Tp. Although these parameters are useful, they do not accurately reflect the waves that are occuring in nature. Ocean waves are a combination of wind sea (short, irregular, locally generated waves) and swell (long, smooth waves, generated by distant storms) and so more parameters are needed to seperate Hs and Tp driven by wind sea and swell, i.e. seperate Hs and Tp parameters for wind sea and swell. Even with seperate parameters for the different types of waves would still not be enough to effectivley characterise waves in the ocean. In order to characterise the detail and complexity of ocean waves a different approach must be used, know as the *spectral* approach. This approach is based on the idea that the sea surface can be characterised as the summation of a large number of harmonic wave components.

# Hydrodynamic modelling
## Introduction

@@

## Delft-3D numerical suite

@@

### Delft-3D WAVE

@@

### Delft-3D FLOW
